---
title: "Thought Starter Visuals"
output: html_document
---
Assignment04 Charts
================

## Variable Width Column Chart

# Using mekko package

1.  Load package
2.  Create data (from cereal dataset)
3.  Plot <https://rdrr.io/cran/mekko/man/barmekko.html>
4.  Final edits -remove x ticks and titles with element\_blank
    (<https://stackoverflow.com/questions/35090883/remove-all-of-x-axis-labels-in-ggplot>)
  - add titles
  - change font to Times New Roman
```{r}
library(mekko)
library(ggplot2)

nutritioninfo <- data.frame(
  brand = c('All_Bran', 'Corn_Flakes', 'Cheerios', 'Fruit_Loops', 'Crispix'),
  calories = c(70, 100, 110, 110, 110),
  rating = c(59.4, 45.9, 50.8, 32.2, 46.9)
)

barmekko(nutritioninfo, brand, calories, rating) +
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + labs(x = "Consumer Rating", y = "Calories per Serving", title = "Calories and Rating for Cereal Brands", caption = "by: Genna Campain") + theme(text= element_text(family = "Times New Roman"))
```

## Bar Chart

Use stat = identity to indicate that I will be giving the values for the
y axis (otherwise R wants to calculate them) Rotate whole chart

```{r}
library(ggplot2)

sugarsinfo <- data.frame(
  brand = c('All_Bran', 'Corn_Flakes', 'Cheerios', 'Fruit_Loops', 'Crispix'),
  sugars = c(5, 2, 1, 13, 3)
)

p <-ggplot(data = sugarsinfo, mapping = aes(x = brand, y = sugars, fill = brand))
p + geom_bar(stat = 'identity') +
  labs(x = "Brand Name", y = "Grams of Sugar", title = "Grams of Sugar In Cereal Brands") + 
  theme(text = element_text(family = "Times New Roman")) +
  coord_flip()
```

## Column Chart

Need to change data format to long using tidyr package Use position
argument to create bars that are next to each other

```{r}
library(ggplot2)

nutrition <- data.frame(
  newbrand = c("All_Bran", "Cheerios", "Fruit_Loops"),
  sugars = c(5, 1, 13),
  protein = c(4, 6, 2),
  fat = c(1, 2, 2),
  fiber = c(9, 2, 1)
)

library(tidyr)
nutrition_long <- gather(nutrition, variable, nutrients, -newbrand )

p <- ggplot(nutrition_long, mapping = aes(x = newbrand, y = nutrients, fill = variable))
p + geom_col(position = position_dodge()) +
  labs(x = "Brand Name", y = "Nutrient Values", title = "Nutrition Information for Various Cereal Brands") +
  theme(text = element_text(family = "Times New Roman"))
```

## Table (with Embedded Charts)

Use formattable package to make more create tables
(<https://renkun-ken.github.io/formattable/>)

```{r}
library(formattable)
cereal <- read.csv("~/Downloads/cereal.csv")

df <- data.frame(
  name = cereal$name,
  calories = cereal$calories,
  protein = cereal$protein,
  fat = cereal$fat,
  fiber = cereal$fiber,
  rating = cereal$rating
)

formattable(df, list(area(col = c(fiber))~normalize_bar("pink", 0.2)))
```
